### 2014-01-16 Draft/example.tex
added new version

\section{Examples}
\label{sec:example}

%We now present a series progressing in complexity to demonstrate our approach. Our examples are from real Java Platform, Micro Edition (JME) formerly known as J2ME and Android API. Both JME and Android use Java as the language of implementation and targeted towards hand-held devices. However, our approach is independent of language of implementation and thus can be used for any similar source and target API.

%First we parse the API documents of source and target API library and store it in intermediate representation for analysis. In particular, we extract class, interface and corresponding method descriptions from API documents. Second, we then create a term vector representation of each class description and method descriptions. Vector space model or term vector model is an algebraic model for representing text documents (and any objects, in general) as vectors of identifiers, such as, for example, index terms. In our case, each word is considered as a term barring the stop words such as (a, the, and ...).

%Finally we use the term vector representation of a method description in a source API to query term vector representation of the the method description in target API. The results are ranked based on the Term Frequency-Inverse Document Frequency (TF-IDF) measure. TF-IDF is a numerical statistic which reflects how important a word is to a document in a collection or corpus. It is often used as a weighting factor in information retrieval and text mining.

%We then collect the top 10 results from target API methods for each source API method. Figure~\ref{fig:excpAPIJ2ME} and Figure~\ref{fig:excpAPIAndroid} shows example of trivially similar API methods. Our search results return the Android API method shown in Figure~\ref{fig:excpAPIAndroid} as a first match for the JME method shown in Figure~\ref{fig:excpAPIJ2ME}. Notice the slightly different description for the methods in JME and Android API. Although, correct this is very trivial mapping. We next present a more complex example.

\begin{figure}[t]
\begin{CodeOut}
\begin{alltt}
\includegraphics[scale=0.4]{Stackoverflow.eps}
\end{alltt}
\end{CodeOut}
\caption{\label{fig:Stackoverflow} The Query posted on Stackoverflow form regrading Amazon S3 REST API}
\end{figure}

\begin{figure}[t]
\begin{CodeOut}
\begin{alltt}
\includegraphics[scale=0.4]{AmzonS3DeleteBucketAPI.eps}
\end{alltt}
\end{CodeOut}
\caption{\label{fig:AmzonS3DeleteBucketAPI} The online API document for \CodeIn{DELETE Bucket} operation in Amazon S3 REST API}
\end{figure}

%Figure~\ref{fig:drawCharAPIJ2ME} and Figure~\ref{fig:drawTextAPIJ2ME} shows example of non-trivially similar API methods. Although, the textual description is similar using text analytics (TF-IDF similarity using term frequency vector), there is difference in type of arguments.

>>>>

\section{Motivating Example}
\label{sec:example}

We now present some real world examples to motivate our approach. In particular, through these examples we demonstrate that developers often overlook the documentation. Thus, the resultant system is inconsistent with the intentions that a developer had in mind initially. This inconsistency oftentimes result in undesirable consequences ranging from developer frustration, customer dissatisfaction, to actual financial losses.

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.4]{Stackoverflow.eps}
\end{center}
\caption{\label{fig:Stackoverflow} The Query posted on Stackoverflow form regrading Amazon S3 REST API}
\end{figure}

For example consider the question asked in \textit{Stack Overflow}~\footnote{\url{http://stackoverflow.com/}} as shown in Figure~\ref{fig:Stackoverflow}. Stack Overflow is a question and answer site for professional and enthusiast programmers. The query is about the delete functionality of a third-party software \CodeIn{S3Fox} to interact with \amazonAPI. In particular, the query complains about an issue in delete bucket functionality of the \CodeIn{S3Fox}. In particular, the issue was because the \CodeIn{S3Fox} developers overlooked the specifications in \amazon. Figure~\ref{fig:AmzonS3DeleteBucketAPI} shows the documentation of delete bucket method. The documents clearly states (outlined in red for clarity) that before deleting the bucket the objects in the buckets must be deleted. Although the issue was fixed but notice that the response on the \textit{Stack Overflow} encouraged the person asking query to switch to another product, thus potentially resulting in a loss of revenue attributed to customer dissatisfaction.

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.4]{AmzonS3DeleteBucketAPI.eps}
\end{center}
\caption{\label{fig:AmzonS3DeleteBucketAPI} The online API document for \CodeIn{DELETE Bucket} operation in Amazon S3 REST API}
\end{figure}

In yet another example a developer points out the financial losses he suffered because he was incorrectly using the previously described delete bucket functionality as shown in Figure~\ref{fig:example2}. The problems in the previously described examples could have been alleviated if developers paid more attention to the documentation. However, as pointed out by Novick et. al~\cite{Novick2006WDP} that developers often overlook the documentation. Furthermore, since these documents are written in natural language they cannot be subjected to machine based verification. Thus, there is need for an approach to translate the constraints described in natural language into a more formal notation. Although, we only use examples from the developer forums and blogs for \amazon\ to motivate our approach. In next section, we briefly discuss the related work in this area.

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.4]{Example2.eps}
\end{center}
\caption{\label{fig:example2} The experience article posted by a developer regarding Amazon S3 REST API}
\end{figure}

### 2014-01-16 Draft/introduction.tex
added new version

%These constraints are mainly expressed in natural language in the service documentation. A widely-adopted strategy [7] by developers to build correct client applications is to first read through the service documentation, trying to memorize the constraints, and then develop client applications accordingly. However, conformance to constraints cannot be assured. In fact, a recent study [14] showed that developers may still make mistakes even when they have been rather familiar with the documentation. 
%
%
%Therefore, it is desirable that client applications are formally verified against these constraints, and violations of each constraint are detected as bugs. However, these verification techniques [8, 9, 14] require formally specified constraints, which are often not readily available, due to the large amount of effort needed to manually specify them. For example, it took one of the authors more than 10 hours to only browse the documentation of the Ebay2 web service operation “AddFixedPriceItem”, let alone the time needed to extract and formalize the constraints
%
%To address these shortcomings we propose a different approach for inferring likely mapping between API's. In particular, we propose the use of Natural Language processing of API documents to infer such mapping.  
%
%  
%API documentation provides developers with useful information about class/interface hierarchies within the software. Additionally, API documents also provides information about how to use a particular method within a class by means of method descriptions. Method descriptions typically describe specifications in terms of the expectations of the method arguments and functionality of method in general.
%
%
%We plan to leverage these method descriptions to find the likely mapping. However, it is not trivial to use natural langauge processing on API documents to infer likely mappings. In particular, our technique addresses the following technical challenges to infer likely mappings:
%
%\begin{enumerate}
%	\item \textit{Programming Keywords}. Method descriptions often contain programming keywords (e.g., \CodeIn{true, null, buffer}), which have a different meaning in the context of programs, in contrast to general linguistics. For instance,\textit{``This method also returns false if path is null''}. In this sentence, words `false' and `null' are nouns in the context of object-oriented languages such as Java and C\#, whereas in general linguistics these words are adjectives. Thus, these keywords need to be handled differently.
%		
%	\item \textit{Semantic Equivalence}. A legal usage in natural language can be described in different words and semantic structures. For instance, consider the following two fragments that describe the similar functionality specification: \textit{``Flushes this data output stream. This forces any buffered output bytes to be written out to the stream.'}' and \textit{``Writes buffered data to the target stream and calls the flush method of the target stream.''}. Thus, there is a need to identify the semantic equivalence of legal usage described in different ways.
%		
%		To address this challenge, we propose a new technique called \textit{equivalence analysis} based on identified grammatical relationships (main nouns and verbs) of a sentence.
%	
%	\item \textit {Partial Functionality}. There are significant number of cases when the functionality in a source API method is broken across multiple methods in target API. For instance \CodeIn{Graphics.drawChar()} method in J2ME API is mapped to methods \CodeIn{Paint.setColor();Canvas.drawText()}in Android API.
%	
%		To address this challenge, we propose a lightweight \CodeIn{Type} analysis.
%		
%\end{enumerate}
%
%
%
%
%In summary, our approach leverages natural language description of API's to infer likely mapping thus facilitating cross API migration of applications. As our approach analyzes API documents in natural language, it can be reused independent of the programming language of the library. To the best of our knowledge, ours is the first approach that analyzes natural language API descriptions to infer likely mapping across API's.
%
%Our paper makes the following major contributions:
%\begin{itemize}
%	\item A technique that effectively infers mapping across source and target API.
%	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{SNLP,SNLP1}, which is a natural language parser to derive the grammatical structure of sentences. An open source implementation of our prototype can be found at our website\footnote{\url{http://research.csc.ncsu.edu/ase/projects/pint/}}. 
%	\item An evaluation of our approach on J2ME and Android API
%\end{itemize}

The rest of the paper is organized as follows. Section~\ref{sec:background} presents the  background on code contracts as well as NLP. Section~\ref{sec:example} presents an real world examples that motivate our approach. Section~\ref{sec:approach} presents our approach. Section~\ref{sec:evaluation} presents evaluation of our approach. Section~\ref{sec:discussion} presents a brief discussion and future work. Section~\ref{sec:related} discusses related work. Finally, Section~\ref{sec:conclusion} concludes.

>>>>

% Introduction needs to tightned up a bit
% Paragraph about typed languages must be moved to background or methodology
% Example might appropriately go in background as well
% Try to fit the goal statement in the introduction
% too long an abstract
% Names of exact tools and citations to them for verification
% Over use of however,
% J2EE document seems to be out of place

Specifications of using an Application Programming Interface (API) of a library play an important role in software reuse.
In addition to guiding the development process by outlining what and how to reuse, 
usage specifications also help in verification process by allowing quality assurance practitioners to test the expected outcome.
Furthermore, if the specifications are formal (machine-readable such as code-contracts),
they can be used in conjunction with the formal analysis tools such as model checkers and runtime verifiers
to automatically reason about the quality of the software.

%Formal specifications of an Application Programming Interface (API) usage are highly desirable.
%because they are the precursor to the formal analysis tools such as model checkers and runtime verifiers.

However, most API's do not have formal specifications.
In contrast, API developers commonly describe correct usage in natural language text in API documents.
Typically, such documents are provided to client-code developers through online access, or are shipped with the API code.
For example, J2EE's API documentation\footnote{\url{http:\\download.oracle.com/javaee/1.7/api/}} is one of the popular API documents.
Typically, an API document will describe the both the constraints on that method parameters as well as the constraints in terms of the methods the must be invoked pre/post the current method.
However, formal analysis tools are not designed to work on specifications written in natural languages.

%May be strike out the first sentence 
%May be strike out the term prohibitevely

A na{\"i}ve solution to address the issue, is to manually convert the natural language API description into formal specifications. 
However, manually writing formal specifications based on natural language text in API documents can be prohibitively time consuming and error prone~\cite{wu2013inferring,RubingerWEB10}. 
For instance, Wu et al.~\cite{wu2013inferring} report that it took one of the authors more than 10 hours to browse the documentation of one method of a web Service API, even before they attempted to formalize the constraints on the method.

%Strike out ``To address the aforementioned issue''
To address the aforementioned issue, we propose a novel approach to infer usage constraints from natural language text of API documents.
We propose new techniques that apply Natural Language Processing (NLP) on natural language text API documents to automatically infer usage constraints.
In particular, we focus on specific type of constraints namely temporal constraints.
A generic temporal relation is defined as \textit{an interpropositional relation that communicates the simultaneity or ordering in time of events or states.}
In terms of API method invocations, we interpret temporal relationships as \textit{`the allowed sequence of invocations of methods'}.
For example, consider the following statement in \amazonAPI\ ``You must initiate a multipart upload before you can upload any part.''
This statement can be interpreted as multipart-upload method must be invoked before invoking any part-upload method in the API.

%Move this paragraph to later sections or may be push later in intro
% make example flow in next paragraph
% Make consistent terminology approach or technique 
Although, in typed languages some sequencing constraints are enforced by type system. 
For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates that (at least one) method ($m'$) be invoked whose return value is of type ($t$).  
However, most temporal constraints are not limited by the type definitions (i.e, requirements on the type of input parameters),
and are currently expressed mostly in natural language in API documents, as described in the example previously.
In a manual investigation, we observed that roughly 12\% of the sentences describing some sort of specification constraints in \amazonAPI\ documentations are temporal constraints related.
%Background on out of how many sentences

% Combine first two sentences
% In contrast, temporal constraints are beyond these parameter constraints. may be use difficult to express using parameter constraints
% Amazon S3 is popularly used web service for simple cloud based storage
Most of the existing approaches focus in inferring method pre-post conditions~\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105,Flanagan:2001:HAA:647540.730008,Buse:2008:ADI:1390630.1390664} in terms of parameter constraints either using static or dynamic analysis techniques.
Furthermore, there is a class of NLP based approaches~\cite{pandita12:inferring, wu2013inferring} that infer constraints from API documents.
However, similar to static and dynamic analysis techniques these approaches focus on parameter constraints as well.  
In contrast, temporal constraints are beyond these parameter constraints.
Temporal constraints, in general focus on rules related to orchestration of methods within an API rather than focusing on the requirements on the input parameters of these methods.   
In particular, our proposed techniques address the following challenges to infer temporal constraints automatically from natural language text.

First, relying just on type information will result in a incomplete list of temporal constraints. 
Furthermore, such constraints although valuable but are already checked by any advanced Integrated Development Environment(IDE) such as eclipse
for a strongly typed language.
The problem is exacerbated in web based API's such as \amazonAPI\ where most of the types are either \CodeIn{integer} or \CodeIn{strings}.

%identified in previous work~\cite{pandita12:inferring} delete and leave the reference
% Add a sentnce stating that we extend previous technique to address the issues 
Second, inferring temporal constraints from the natural language text itself is challenging. 
There are existing challenges in NLP for software engineering domain namely \textit{ambiguity}, \textit{programming keywords}, and \textit{semantic equivalence} identified in previous work~\cite{pandita12:inferring}.
In addition to these challenges, we have an added challenge of identifying the method referenced in the natural language text to infer temporal constraint.
Recall, the description sentence ``You must initiate a multipart upload before you can upload any part.''
In this sentence, phrases ``multipart upload'' and ``upload any part'' refer to individual methods in the API.
Identifying these phrases as method invocation instances require domain dictionaries.
Ad-hoc constructing these dictionaries is prohibitively time and resources intensive.
To address this challenge we propose to build domain-dictionaries systematically from API documents themselves.

%Furthermore, I propose to evaluate the effectiveness of proposed work on real world API's: 1) Java 7 and 2) Amazon S3 REST API. The former is generic language API, while the later is a web based API directed towards cloud-based data storage. The temporal constraints inferred for Java 7 will be compared with the existing approaches to evaluate the effectiveness of proposed work. In contrast, Amazon S3 REST API (relatively recent) representative of the class of API's where neither source code of API nor enough usage examples are available.

%To evaluate our proposed approach, we applied \tool\ to infer temporal constraints from 
%commonly used package \CodeIn{java.io} from JDK API and Amazon S3 REST API.
%Our evaluation results show that \tool\ achieves an average of PP\% precision and RR\% recall
%in inferring TT temporal constraints from more than ZZZZ sentences of API documents.

%Software reuse is commonly practiced since the advent of software development~\cite{FrakesIEEETran05}. Software reuse facilitates development of larger, more complex, and timely-delivered software systems~\cite{GaffneySE92}. To determine what and how to reuse, specifications of reusable software libraries play an important role. In the absence of specifications, developers may write code that is inconsistent with the expectations of libraries. As a result, not only such code is of inferior quality and contains faults, the added cost of debugging and correcting such faulty code could also defeat the purpose of reusing software.

% talk about mining approaches 
In summary, the proposed work leverages natural language description of API's to infer temporal constraints of method invocations.
As the proposed work analyzes API documents in natural language, it can be reused independent of the programming language of the library.
Additionally, our approach complements existing mining based approaches~\cite{buse2012synthesizing, thummalapenta07parseweb, Wang:2013:MSR, Zhong:2009:MMR} that partially address the problem by mining for common usage patterns.
The proposed work in general, makes the following contributions:
%However, all of these approaches rely on the availability of the source code that use API methods under investigation.
%Furthermore, these approaches are limited by both the quantity as well as quality of data set (source code) available.
%To address the limitation we propose to extend the natural language infrastructure developed previously~\cite{pandita12:inferring,pandita2013whyper} to focus specifically on the temporal constraints.

%Use consistent term technique or approach
%Methodology for generating domain dictionaries 
\begin{itemize}
	\item A NLP based approach that infers temporal constraints of method invocations.
	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03,SNLP1}, which is a natural language parser to derive the grammatical structure of sentences.
	An open source implementation of the prototype will be made available publicly. 
	\item An evaluation of proposed approach on Java 7 and Amazon S3 REST API
\end{itemize}

The rest of the paper is organized as follows.
Section~\ref{sec:example} presents an real world examples that motivate our approach.
Section~\ref{sec:related} discusses related work in this area.
Section~\ref{sec:background} presents the  background on code contracts as well as NLP.
Section~\ref{sec:approach} presents our approach.
Section~\ref{sec:evaluation} presents evaluation of our approach.
Section~\ref{sec:discussion} presents a brief discussion and future work.
Finally, Section~\ref{sec:conclusion} concludes.

% how well does the NLP based technique augument the type based temporal constraints

### 2014-01-16 Draft/related.tex
added new version

Design by contracts has been an influential concept in the area of software engineering in the past decade. A significant amount of work has been done in automated inference of code contracts. There are existing approaches that statically or dynamically extract code contracts~\cite{csallner08dysy, NimmerE02:ISSTA, Tillmann:2006:DLM:2105385.2105433}. However, a combination of developer written and automatically inferred contracts seems to be the most effective approach~\cite{FrakesIEEETran05,Polikarpova2009ISSTA}. Since developers describe the specifications in the method descriptions, we believe that our approach can work in conjunction with existing approaches towards extracting a comprehensive set of code contracts for a method. Furthermore, Wei et al.~\cite{WeiICSE11}demonstrated that dynamic contract inference performed better when provided with an initial set of seed contracts.

There are existing approaches that infer code-contract-like specifications (such as behavioral model, algebraic specifications, and exception specifications) either dynamically~\cite{Ghezzi:2009:SIB:1555001.1555057,Henkel07documentation,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Buse:2008:ADI:1390630.1390664,FrakesIEEETran05} from source code and binaries. In contrast, our approach infers specifications from the natural language text in API documents, thus complementing these existing approaches when the source code or binaries of the API library is not available.

NLP techniques are increasingly applied in the software engineering domain. NLP techniques have been shown to be useful in requirements engineering~\cite{Gervasi2005,Sinha2009,Sinha2010}, usability of API documents~\cite{Dekel2009}, and other areas~\cite{Little2009,Zhou2008}. We next describe most relevant approaches.

Xiao et al.~\cite{XiaoFSE2012} use shallow parsing techniques to infer Access Control Policy (ACP) rules from natural language text in use cases. The use of shallow parsing techniques works well on natural language texts in use cases, owing to well formed nature of sentences in use case descriptions. In contrast, often the sentences in API documents are not well formed. Additionally, their approach does not deal with programming keywords or identifiers, which are often mixed within the method descriptions in API documents.

\
~\cite{pandita12:inferring}
~\cite{pandita13:WHYPER}

Zhong et al.~\cite{zhong09SE} employ NLP and ML techniques to infer resource specifications from API documents. Their approach uses machine learning to automatically classify such rules. In contrast, we attempt to parse sentences based on semantic templates and demonstrate that such an approach preforms reasonably well. Tan et al.~\cite{TanSOSP07} applied an NLP and Machine Learning (ML) based approach to test Javadoc comments against implementations. However, their approach specifically focuses on null values and related exceptions, thus limiting the application scope. In contrast, our approach infers generic specifications from API documents. In particular, our approach already produces FOL representation of the specifications that can be used to test implementations. Furthermore, the performance of the preceding ML-based approaches is dependent on the quality of the training sets used for ML. In contrast, our approach is independent of such training set and thus can be easily extended to target respective problems addressed by these approaches.

Among other works described in ~\cite{RobillardIEEEtranSE13}, Mining API Mapping (MAM)~\cite{Zhong2010ICSE} is most directly related to our work. MAM mines API mapping relations across different languages for language migration, however they do little in terms of mining usage constraints of methods.

%Web Query~\cite{Zheng2011FSE}

%\textbf{Library migration}. With evolution of libraries, some APIs may become incompatible across library versions. To address this problem, Henkel and Diwan ~\cite{csallner08dysy} proposed an approach that captures and replays API refactoring actions to update the client code. Xing and Stroulia [17] proposed an approach that recognizes the changes of APIs by comparing the differences between two versions of libraries. Balaban et al. [2] proposed an approach to migrate client code when mapping relations of libraries are available. In contrast to these approaches, our approach focuses on mapping relations of APIs across different languages. In addition, since our approach uses ATGs to mine API mapping relations, our approach can also mine mapping relations between API methods with different parameters or between API methods whose functionalities are split among several API methods in the other language.

>>>>

// "In contrast" switch up the wording a little bit

Our proposed approach touches a few research areas such as software verification,  NLP on software engineering artifacts, and document augmentation. We next discuss relevant work pertinent to our proposed approach in these areas.

\textbf{Code Contracts - Formal Specifications}
// Define temporal constraints distinction
Design by contracts has been an influential concept in the area of software engineering in the past decade. A significant amount of work has been done in automated inference of code contracts. There are existing approaches that statically or dynamically extract code contracts~\cite{csallner08dysy,NimmerE02:ISSTA,Tillmann:2006:DLM:2105385.2105433}. However, a combination of developer written and automatically inferred contracts seems to be the most effective approach~\cite{Polikarpova2009ISSTA,Flanagan:2001:HAA:647540.730008}. Furthermore, there are existing approaches that infer code-contract-like specifications (such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan:2001:HAA:647540.730008,Buse:2008:ADI:1390630.1390664} from source code and binaries. In contrast, the approach presented in this work infers specifications from the natural language text in API documents, thus complementing these existing approaches when the source code or binaries of the API library is not available.

\textbf{NLP in Software Engineering}

NLP techniques are increasingly applied in the software engineering domain. NLP techniques have been shown to be useful in requirements engineering ~\cite{Sinha2009,Sinha2010,Gervasi2005}, usability of API documents~\cite{Dekel2009}, and other areas~\cite{Zhou2008,Little2009,pandita13:WHYPER}. We next describe the most relevant approaches.

\textit{1. Access Control Policies}: Xiao et al.~\cite{XiaoFSE2012} and Slankas et al.~\cite{johnSlankasPASSAT13} use shallow parsing techniques to infer Access Control Policy (ACP) rules from natural language text in use cases. The use of shallow parsing techniques works well on natural language texts in use cases, owing to well formed structure of sentences in use case descriptions. In contrast, often the sentences in API documents are not well formed. Additionally, these approaches do not deal with programming keywords or identifiers, which are often mixed within the method descriptions in API documents.

\textit{2. Resource Specifications}: Zhong et al.~\cite{zhong09SE} employ NLP and  Machine Learning (ML) techniques to infer resource specifications from API documents. Their approach uses machine learning to automatically classify such rules. In contrast, we attempt to parse sentences based on semantic templates and demonstrate that such an approach preforms reasonably well. Furthermore, the performance of the approach is dependent on the quality of the training sets used for ML. In contrast, approach presented in this work is independent of such training set and thus can be easily extended to target respective problems addressed by these approaches.

\textit{3. Code Comments}: Tan et al.~\cite{TanSOSP07} and Hwei-Tan et al.~\cite{tcomment} applied an NLP and ML  based approach on code comments/ Javadoc comments to detect mismatches between these comments and implementations. They rely on predefined rule templates targeted towards method invocation and lock related comments, thus limiting their scope both in terms of application area as well as language used in the comments. In contrast, approach presented in this report relies on generic natural language based templates thus relaxing the restriction on the style of the language used to describe specifications.

\textit{4. API Description}: Most closely related work to the approach presented here is Pandita et al.~\cite{pandita12:inferring} work on inferring parameter constraints from method descriptions in the API documents. In contrast this approach deals with the temporal constraints. The approach presented here is a significant extension to the infrastructure used in the previous work as documented in Section~\ref{sec:approach}.

\textbf{Augmented Documentation}

Another related field has been that of improving the documentation related to an software API~\cite{Dekel2009,tan2011acomment}. We next describe most relevant approaches. Dekel et al.~\cite{Dekel2009}, were the first to create a tool namely eMoose, an Eclipse~\footnote{\url{http://www.eclipse.org/}} based plug-in that allowed developers to create directives( way of marking the specification sentences) in the default documentation. These directives are highlighted whenever they are displayed in the eclipse environment. Lee et al.~\cite{lee2012towards} improved upon their work by providing a formalism to the directives proposed by Dekel et al.~\cite{Dekel2009}, thus allowing tool based verification. However, a developer has to manually annotate such directives. In contrast, our proposed approach both identifies the sentences pertaining to temporal constraints and infers the temporal constraints automatically.

In next section, we briefly introduce the NLP techniques used by our approach.

%\textbf{Program Comprehension}
%
%With respect to program comprehension there are existing techniques that assist in building domain specific ontologies~\cite{Zhou2008}. Furthermore, there are existing approaches~\cite{sridhara2011ICPC,robillard1986schematic} that automatically infer natural language documentation from source code. These approaches would immensely help in comprehension of the functionality of an application. However inherent dependency on source code to generate such documents poses a problem in cases, where source code is not available. We next describe some of these approaches 
%
%\begin{itemize}
% \item Sridhara et al.~\cite{sridhara2011ICPC} use data-flow analysis on the method variables to determine the set of statements that represent the computational intent of the method. The data flow analysis is then used to determine the relation of these statements to the method parameters. These realtions are then thn used to generate the natural language parameter documentation using predefined templates.
%
% \item Zhang et al.~\cite{zhang2011automated} present an approach to generate the explanatory document in the form of code comments explaining the failure of the test case. They first instrument the failing test case. They then use statistical algorithm on the different execution traces of the failing test case to determine a relatively small subset of the suspicious statements along with the objects that need correction for successful execution of test case. Finally, the identified objects that need correction for successful execution of the test case are used to generate the explanatory comments using predefined templates on the generalized properties of the object. For instance, \CodeIn{x == null} becomes \textit{x is set to:null}.
%
% \item Buse et al.~\cite{Buse:2008:ADI:1390630.1390664} use source mining source code repositories to generate usage patterns of an API. They argue that availability of actual usable code examples serves as a better documentation assisting developers in understating the usage of API. They propose the clustering of the uses of an API in the open source repositories based on path information. They then propose type abstraction on the clusters to come up with a usage document. 
%\end{itemize}
